\sysfull

### 2018-04-10 paper/paper.tex
made paper OOPSLA 2018 style complaint

\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmConference[Submitted to OOPSLA'18]{ACM SIGPLAN Conference on Programming Language Design and Implementation}{June 18--22, 2018}{Philadelphia, PA, USA}

\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\setcopyright{none}

%% Some recommended packages.
%\usepackage{booktabs}   %% For formal tables: http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions http://ctan.org/pkg/subcaption
%\usepackage[normalem]{ulem}
%\usepackage{float}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{hyphenat}

\usepackage{titlesec}

%\titlespacing{\section}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsection}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsubsection}{0pt}{0.5\baselineskip}{\parskip}
\titlespacing{\section}{2pt}{0.8\baselineskip}{\parskip}
\titlespacing{\subsection}{2pt}{0.6\baselineskip}{\parskip}
\titlespacing{\subsubsection}{2pt}{0.6\baselineskip}{\parskip}

\setlength{\textfloatsep}{5pt}% Remove \textfloatsep

%\usepackage[keeplastbox]{flushend} %Brandon: this broke the build for me
%Added for sub-float package from jpaper.cls - will check later
%\RequirePackage[font={normalsize,sf,bf}]{caption}
%\RequirePackage[position=bottom]{subfig}
%\captionsetup[table]{aboveskip=0.5em, belowskip=0.5em}
%\captionsetup[figure]{aboveskip=0.5em, belowskip=0em}
\captionsetup[subfloat]{font={small,sf}}

@@

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Adaptive Task Coalescing $\ldots$}
\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

\title[\sysmed]{\sysfull}

@@

%\author{Kiwan Maeng}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Carnegie Mellon University}
%	\streetaddress{4720 Forbes Avenue}
%   \city{Pittsburgh} 
%	\state{PA} 
%	\postcode{15213}
%}
%\email{kmaeng@andrew.cmu.edu}

%\author{Alexei Colin}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Carnegie Mellon University}
%	\streetaddress{4720 Forbes Avenue}
%	\city{Pittsburgh} 
%	\state{PA} 
%	\postcode{15213}
%}
%\email{acolin@andrew.cmu.edu}

%\author{Brandon Lucia}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Carnegie Mellon University}
%	\streetaddress{4720 Forbes Avenue}
%	\city{Pittsburgh} 
%	\state{PA} 
%	\postcode{15213}
%}
%\email{blucia@andrew.cmu.edu}

%\author{Amjad Yousef Majid}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Delft University of Technology}
%	\streetaddress{Mekelweg 4}
%	\city{Delft, The Netherlands} 
%	\state{Zuid Holland} 
%	\postcode{2628\,CD}
%}
%\email{a.y.majid@tudelft.nl}

%\author{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Delft University of Technology}
%	\streetaddress{Mekelweg 4}
%	\city{Delft, The Netherlands} 
%	\state{Zuid Holland} 
%	\postcode{2628\,CD}
%}
%\email{k.s.yildirim@tudelft.nl}

%\author{Przemys{\l}aw Pawe{\l}czak}
%\authornote{}
%\orcid{}
%\affiliation{%
%	\institution{Delft University of Technology}
%	\streetaddress{Mekelweg 4}
%	\city{Delft, The Netherlands} 
%	\state{Zuid Holland} 
%	\postcode{2628\,CD}
%}
%\email{p.pawelczak@tudelft.nl}

%\renewcommand{\shortauthors}{A. Y. Majid et al.}

@@

%\begin{CCSXML}
%	<ccs2012>
%	<concept>
%	<concept_id>10010520.10010553.10010562.10010564</concept_id>
%	<concept_desc>Computer systems organization~Embedded 
%	software</concept_desc>
%	<concept_significance>500</concept_significance>
%	</concept>
%	<concept>
%	<concept_id>10010520.10010575.10010578</concept_id>
%	<concept_desc>Computer systems organization~Availability</concept_desc>
%	<concept_significance>300</concept_significance>
%	</concept>
%	<concept>
%	<concept_id>10011007.10010940.10010941.10010949.10010957.10010688</concept_id>
%	<concept_desc>Software and its engineering~Scheduling</concept_desc>
%	<concept_significance>300</concept_significance>
%	</concept>
%	<concept>
%	<concept_id>10011007.10010940.10010941.10010949.10010965</concept_id>
%	<concept_desc>Software and its engineering~Communications 
%	management</concept_desc>
%	<concept_significance>300</concept_significance>
%	</concept>
%	<concept>
%	<concept_id>10011007.10010940.10010971.10010564</concept_id>
%	<concept_desc>Software and its engineering~Embedded 
%	software</concept_desc>
%	<concept_significance>300</concept_significance>
%	</concept>
%	</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded software}
%\ccsdesc[300]{Computer systems organization~Availability}
%\ccsdesc[300]{Software and its engineering~Scheduling}
%\ccsdesc[300]{Software and its engineering~Communications management}
%\ccsdesc[300]{Software and its engineering~Embedded software}

%\keywords{Energy harvesting, transient operation, operating system}

@@

\input{coalescing}
% \input{newCoalescing}

@@

%\section{Discussion}
%\label{sec:discussion}

%\input{discussion}

@@

\bibliographystyle{ACM-Reference-Format}
%\bibliographystyle{plain}
\bibliography{bib}

>>>>

\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{OOPSLA} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

\setcopyright{none}

\usepackage{booktabs}   % For formal tables: http://ctan.org/pkg/booktabs
\usepackage{subcaption} % For complex figures with subfigures/subcaptions http://ctan.org/pkg/subcaption
\usepackage{soul}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm} % environment for the algorithm code (like figure and table)
\usepackage{algorithmicx} % write the pseudo code
\usepackage[noend]{algpseudocode} % layout of the pseudo code
\usepackage{tikz} % needed for: tikz pics
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{hyphenat}

@@

%\usepackage[normalem]{ulem}
%\usepackage{float}

%\usepackage{titlesec} %P{rzemek: ommented, has conflict https://tex.stackexchange.com/questions/321999/conflict-between-makeuppercase-in-title-formatting-and-usepackagexcolor

%\titlespacing{\section}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsection}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\subsubsection}{0pt}{0.5\baselineskip}{\parskip}
%\titlespacing{\section}{2pt}{0.8\baselineskip}{\parskip}
%\titlespacing{\subsection}{2pt}{0.6\baselineskip}{\parskip}
%\titlespacing{\subsubsection}{2pt}{0.6\baselineskip}{\parskip}

%\setlength{\textfloatsep}{5pt}% Remove \textfloatsep

%\usepackage[keeplastbox]{flushend} %Brandon: this broke the build for me
%Added for sub-float package from jpaper.cls - will check later
%\RequirePackage[font={normalsize,sf,bf}]{caption}
%\RequirePackage[position=bottom]{subfig}
%\captionsetup[table]{aboveskip=0.5em, belowskip=0.5em}
%\captionsetup[figure]{aboveskip=0.5em, belowskip=0em}
%\captionsetup[subfloat]{font={small,sf}}

@@

\newcommand{\transition}{{\tt next\_task}\xspace}
\newcommand{\sys}{Coala\xspace}
\newcommand{\sysmed}{\sys: Adaptive Task Coalescing for Intermittent Computing $\ldots$}
\newcommand{\sysfull}{\sys: Adaptive Task Coalescing for Intermittent Computing on Energy-harvesting Devices}
%newcommand{\sysfull}{\sys: Efficient Task-based Intermittent Computing with Adaptive Task Coalescing and Memory Virtualization} %Old title

@@

%% Title information
\title[\sysmed]{\sysfull}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
%\titlenote{}             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
%\subtitle{}                     %% \subtitle is optional
%\subtitlenote{}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

@@

\author{Kiwan Maeng}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
   \city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{kmaeng@andrew.cmu.edu}

\author{Alexei Colin}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
	\city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{acolin@andrew.cmu.edu}

\author{Brandon Lucia}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Carnegie Mellon University}
	\streetaddress{4720 Forbes Avenue}
	\city{Pittsburgh} 
	\state{PA} 
	\postcode{15213}
}
\email{blucia@andrew.cmu.edu}

\author{Carlo Delle Donne}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Van Mourik Broekmanweg 6}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,XE}
}
\email{c.delledonne@student.tudelft.nl}

\author{Amjad Yousef Majid}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Van Mourik Broekmanweg 6}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,XE}
}
\email{a.y.majid@tudelft.nl}

\author{Kas{\i}m Sinan Y{\i}ld{\i}r{\i}m}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Van Mourik Broekmanweg 6}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,XE}
}
\email{k.s.yildirim@tudelft.nl}

\author{Przemys{\l}aw Pawe{\l}czak}
\authornote{}
\orcid{}
\affiliation{%
	\institution{Delft University of Technology}
	\streetaddress{Van Mourik Broekmanweg 6}
	\city{Delft, The Netherlands} 
	\state{Zuid Holland} 
	\postcode{2628\,XE}
}
\email{p.pawelczak@tudelft.nl}

\renewcommand{\shortauthors}{A. Y. Majid et al.}

@@

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010520.10010553.10010562.10010564</concept_id>
	<concept_desc>Computer systems organization~Embedded 
	software</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010575.10010578</concept_id>
	<concept_desc>Computer systems organization~Availability</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010941.10010949.10010957.10010688</concept_id>
	<concept_desc>Software and its engineering~Scheduling</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010941.10010949.10010965</concept_id>
	<concept_desc>Software and its engineering~Communications 
	management</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010971.10010564</concept_id>
	<concept_desc>Software and its engineering~Embedded 
	software</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded software}
\ccsdesc[300]{Computer systems organization~Availability}
\ccsdesc[300]{Software and its engineering~Scheduling}
\ccsdesc[300]{Software and its engineering~Communications management}
\ccsdesc[300]{Software and its engineering~Embedded software}

\keywords{Energy harvesting, transient operation, operating system}

@@

%\input{coalescing}
\input{newCoalescing}

@@

\section{Discussion}
\label{sec:discussion}

\input{discussion}

@@

\bibliographystyle{ACM-Reference-Format}
%\bibliographystyle{plain}
\bibliography{bib}
\citestyle{acmauthoryear}
